Differentially Private Bayesian Inference

### 2018-03-26 main.tex
dilation update
update proof of laplace dilation property.

\documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel}
% Recommended, but optional, packages for figures and better typesetting:
\usepackage{mathtools,amssymb}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}
% \renewcommand\qedsymbol{$\blacksquare$}
% \theoremstyle{plain}
%   \newtheorem{thm}{Theorem}
% \theoremstyle{definition}
%   \newtheorem*{proof1}{Proof of Theorem \ref{Fermat}}
% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}
% \newenvironment{proofof}[1]{\par
%   \pushQED{\qed}%
%   \normalfont \topsep6\p@\@plus6\p@\relax
%   \trivlist
%   \item[\hskip\labelsep
%         \bfseries
%     Proof of #1\@addpunct{.}]\ignorespaces
% }{%
%   \popQED\endtrivlist\@endpefalse
% }
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\input{macros}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

@@

	\item \textbf{case 2: $\lambda < 0$}
	\begin{equation*}
	\begin{split}
	\because\	& \frac{h(e^{\lambda} z)}{h(z)} = exp(|z|(1 - e^{\lambda})) \leq |\lambda|\\
	\therefore\	& ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}) \leq |z||\lambda|\\
	\end{split}
	\end{equation*}

	We consider an event $G = \{z |\ |z|\leq log(\frac{1}{\delta}) \}$. Under this event, we have:

	\begin{equation*}
	|z||\lambda| \leq log(\frac{1}{\delta})|\lambda| \leq log(\frac{1}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \leq \frac{\epsilon}{2}.
	\end{equation*}

	We start from the thing we want to proof:

	\begin{equation*}
	Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} \in e^{\lambda} S] + \frac{\delta}{2}
	\end{equation*}

	\begin{equation*}
	Pr[z \in S] \leq Pr[z \in S  G]
	\end{equation*}

>>>>

\documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel}
% Recommended, but optional, packages for figures and better typesetting:
\usepackage{mathtools,amssymb}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{mdframed}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}
% \renewcommand\qedsymbol{$\blacksquare$}
% \theoremstyle{plain}
%   \newtheorem{thm}{Theorem}
% \theoremstyle{definition}
%   \newtheorem*{proof1}{Proof of Theorem \ref{Fermat}}
% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}
% \newenvironment{proofof}[1]{\par
%   \pushQED{\qed}%
%   \normalfont \topsep6\p@\@plus6\p@\relax
%   \trivlist
%   \item[\hskip\labelsep
%         \bfseries
%     Proof of #1\@addpunct{.}]\ignorespaces
% }{%
%   \popQED\endtrivlist\@endpefalse
% }
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\input{macros}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

@@

	\item \textbf{case 2: $\lambda < 0$}
	% \begin{equation*}
	% \begin{split}
	% \because\	& \frac{h(e^{\lambda} z)}{h(z)} = exp(|z|(1 - e^{\lambda})) \leq |\lambda|\\
	% \therefore\	& ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}) \leq |z||\lambda|\\
	% \end{split}
	% \end{equation*}

	% We consider an event $G = \{z |\ |z|\leq log(\frac{1}{\delta}) \}$. Under this event, we have:

	% \begin{equation*}
	% |z||\lambda| \leq log(\frac{1}{\delta})|\lambda| \leq log(\frac{1}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \leq \frac{\epsilon}{2}.
	% \end{equation*}

	% Also, from the Laplace distribution property we have:

	% \begin{equation*}
	% Pr[G] \geq 1 - \delta ;
	% \end{equation*}

	% \begin{equation*}
	% Pr[\overline{G}] \leq \delta .
	% \end{equation*}

	% We start from the thing we want to proof:

	% \begin{equation*}
	% Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2};
	% \end{equation*}

	% \begin{equation*}
	% \begin{split}
	% \underset{z \thicksim Lap(1)}{Pr}[z \in S] \leq & Pr[z \in S \cap G] + Pr[z \in \overline{G}]\\
	% \leq 	& Pr[z \in S \cap G] + \delta\\
	% \leq 	& e^{|z||\lambda|} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S \cap G] + \delta \\
	% \leq	& e^{|z||\lambda|} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S] + \delta\\
	% \leq	& e^{\frac{\epsilon}{2}} \underset{z \thicksim Lap(e^{\lambda})}{Pr}[z \in S] + \delta\\
	% =		& e^{\frac{\epsilon}{2}} \underset{z \thicksim Lap(1)}{Pr}[z \in e^{\lambda} S] + \delta\\
	% \end{split}
	% \end{equation*}
	From integral property, we firstly have:

	\begin{equation*}
	\frac{Pr[z\in e^{\lambda} S]}{Pr[z\in S]} 
	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}} 
	= \frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} 
	= e^{\lambda}e^{|z|(1 - e^{\lambda})}
	\end{equation*}

	\begin{equation*}
	\begin{split}
	\because\	& 1 - e^{\lambda} \leq |\lambda| \\
	\therefore\	& \ln (\frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} )
	\leq \lambda + |z||\lambda|\\
	\because\	& \lambda < 0\\
	\therefore\	& \ln (\frac{h(e^{\lambda} z) e^{\lambda}}{h(z)} )
	\leq |z||\lambda|\\
	\end{split}
	\end{equation*}

	By setting $h'(z) = e^{\lambda} h(e^{\lambda} z)$, we can get:

	\begin{equation*}
	\begin{split}
	&\ln(\frac{h'(z)}{h(z)}) \leq |z||\lambda|\\
	\Rightarrow & h'(z)\leq  e^{|z||\lambda|}h(z)
	\end{split}
	\end{equation*}

	By exchanging the notation of $h'$ and $h$, we have:

	\begin{equation*}
	h(z) \leq e^{|z||\lambda|}h'(z)
	\end{equation*}

	i.e.

	\begin{equation*}
	\underset{z \thicksim h}{Pr}[z \in S] 
	\leq  e^{|z||\lambda|}\underset{z \thicksim h'}{Pr}[z \in S]
	= e^{|z||\lambda|}\underset{z \thicksim h}{Pr}[z \in e^{\lambda} S]
	\end{equation*}

	We consider an event $G = \{z |\ |z|\leq log(\frac{2}{\delta}) \}$. Under this event, we have:

	\begin{equation*}
	\begin{split}
	|z||\lambda| 	& \leq log(\frac{2}{\delta})|\lambda|\\
					& \leq log(\frac{2}{\delta}) \beta\\
					&\leq log(\frac{2}{\delta})\frac{\epsilon}{2 log(\frac{3}{\delta})} \\
					&\leq \frac{\epsilon}{2}.
	\end{split}
	\end{equation*}

	Then:

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim h}{Pr}[z \in S \cap G] 
	& \leq  e^{|z||\lambda|}\underset{z \thicksim h'}{Pr}[z \in S\cap G]\\
	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S \cap G]\\
	\end{split}
	\end{equation*}

	We also have:

	\begin{equation*}
	Pr[\overline{G}] = Pr[|z| > log(\frac{2}{\delta})] = exp(-log(\frac{2}{\delta})) = \frac{\delta}{2}
	\end{equation*}

	Then, we can get

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim h}{Pr}[z \in S] 
	& \leq \underset{z \thicksim h}{Pr}[z \in S\cap G] + \underset{z \thicksim h}{Pr}[z \in \overline{G}]\\
	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S \cap G] + \frac{\delta}{2}\\ 
	& \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim h'}{Pr}[z \in S] + \frac{\delta}{2}\\ 
	& = e^{\frac{\epsilon}{2}} \underset{z \thicksim h}{Pr}[z \in e^{\lambda} S] + \frac{\delta}{2}\\ 
	\end{split}
	\end{equation*}
